	\subsubsection{testcase01-ts09oeSollicitateCrisisHandling-actActivator.outactActivator.oeSollicitateCrisisHandling}
	\label{TM-testcase01-ts09oeSollicitateCrisisHandling-actActivator.outactActivator.oeSollicitateCrisisHandling}

	The \msrcode{testcase01-ts09oeSollicitateCrisisHandling-actActivator.outactActivator.oeSollicitateCrisisHandling} has the following properties:

	\begin{teststepmodel}
		\addheading{Test Step}
		\adddoublerow{ts09oeSollicitateCrisisHandling}{test the proactive sollication to handle an alert.}
		
		
		\addrowheading{Test Sent Message}
		\addnumberedsinglerow{TSM}{
		\vspace{-0.5cm}
		\begin{description}
			\item[] \textbf{out:TheActor}
			\item[] \textbf{sends to system}
			\item[] \textbf{\hyperlink{actActivator.outactActivator.oeSollicitateCrisisHandling}{actActivator.outactActivator.oeSollicitateCrisisHandling} ()}
		\end{description}}
		
		
		
		\addrowheading{Variables}
		\addnumbereddoublerow{V}{TheActor:icrash.environment.actActivator}
		{proactive actor responsible of triggering sollicitation functionality.}

		\addrowheading{Constraints}
		\addnumberedsinglerow{C}{TheActor is any instance existing in the current environment status. It is expected to exist at least one.}

		\addrowheading{Oracle Variables}
		\addnumbereddoublerow{OV}{TheAdministrator:actAdministrator}
			{actAdministrator actors can be sollicitated to handle alerts.}
		\addnumbereddoublerow{OV}{TheCoordinator:actCoordinator}
			{actCoordinator actors can be sollicitated to handle alerts.}
		\addnumbereddoublerow{OV}{AMessageForCrisisHandlers:ptString}
			{messages sent to sollicitated actors are of type ptString.}

		\addrowheading{Oracle Constraints}
		\addnumberedsinglerow{OC}{TheAdministrator is any instance existing in the current environment status. It is expected to exist at least one.}
		\addnumberedsinglerow{OC}{TheCoordinator is any instance existing in the current environment status. It is expected to exist at least one.}
		\addnumberedsinglerow{OC}{AMessageForCrisisHandlers is equal to the ptString 'There are alerts pending since more than the defined delay. Please REACT !'}
		\addnumberedsinglerow{OC}{TheCoordinator and TheAdministrator have received the message AMessageForCrisisHandlers.}
	\end{teststepmodel}
	
	
	
	
	
