	\subsubsection{testcase01-ts07oeAlert1-actComCompany.outactComCompany.oeAlert}
	\label{TM-testcase01-ts07oeAlert1-actComCompany.outactComCompany.oeAlert}

	The \msrcode{testcase01-ts07oeAlert1-actComCompany.outactComCompany.oeAlert} has the following properties:

	\begin{teststepmodel}
		\addheading{Test Step}
		\adddoublerow{ts07oeAlert1}{tests the declaration of a new alert functionality.}
		
		
		\addrowheading{Test Sent Message}
		\addnumberedsinglerow{TSM}{
		\vspace{-0.5cm}
		\begin{description}
			\item[] \textbf{out:TheActor}
			\item[] \textbf{sends to system}
			\item[] \textbf{\hyperlink{actComCompany.outactComCompany.oeAlert}{actComCompany.outactComCompany.oeAlert} (AetHumanKind, AdtDate, AdtTime, AdtPhoneNumber, AdtGPSLocation, AdtComment)}
		\end{description}}
		
		
		
		\addrowheading{Variables}
		\addnumbereddoublerow{V}{TheActor:actComCompany}
		{actComCompany actors transfer alert declaration messages.}

		\addrowheading{Constraints}
		\addnumberedsinglerow{C}{TheActor is any instance existing in the current environment status. It is expected to exist at least one.}
		\addnumberedsinglerow{C}{AetHumanKind is equal to witness}
		\addnumberedsinglerow{C}{AdtDate is equal to the 26th of November 2017}
		\addnumberedsinglerow{C}{AdtTime is equal to 10:10:16 using a 24-hours.}
		\addnumberedsinglerow{C}{AdtPhoneNumber is equal to the ptString value '+3524666445252'.}
		\addnumberedsinglerow{C}{AdtGPSLocation is equal to (49.627675 , 6.159590).}
		\addnumberedsinglerow{C}{AdtComment is equal to '3 cars involved in an accident.'}


		\addrowheading{Oracle Constraints}
		\addnumberedsinglerow{OC}{AdtSMS is equal to the ptString 'Your alert has been registered. We will handle it and keep you informed'.}
		\addnumberedsinglerow{OC}{AdtSMS is sent to the phone number AdtPhoneNumber using the communication company having sent the alert using its ieSmsSend input message.}
	\end{teststepmodel}
	
	
	
	
	
