\subsection{Primary types - Datatypes types descriptions}





The table below is providing comments on the graphical views given for the datatype types of the primary types.


\begin{datadictionary}
\addheading{Datatypes}

\adddoublerow{dtAddOrDelete}{}
\adddoubletwocolumnrow{attribute}{\msrcode{attAdd: ptBoolean}}{}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{}
\adddoublerow{dtAlertID}{ A string used to identify alerts.}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid alert identifiers.}
\adddoublerow{dtComment}{a datatype made of a string value used to receive,store and send textual information about crisis and alerts.}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid comments.}
\adddoublerow{dtCoordinatorID}{A string used to identify coordinators.}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid coordinators identifiers.}
\adddoublerow{dtCrisisID}{ A string used to identify crisis.}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid crisis identifiers.}
\adddoublerow{dtGPSLocation}{used to define coordinates of geograpical positions on earth. It is defined a couple made of a latitude and a longitude.}
\adddoubletwocolumnrow{attribute}{\msrcode{latitude: dtLatitude}}{for the latitude part of the coordinate.}
\adddoubletwocolumnrow{attribute}{\msrcode{longitude: dtLongitude}}{for the longitude part of the coordinate.}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which couples are considered as valid dtGPSLocation values.}
\adddoubletwocolumnrow{operation}{\msrcode{isNearTo(AGPSLocation:dtGPSLocation):ptBoolean}}{used to determine if locations are considered enough close to be treated as equivalent in the application domain context.}
\adddoublerow{dtLatitude}{used to define a latitude value of a geograpical positions on earth.}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid dtLatitude.}
\adddoublerow{dtLogin}{ a login string used to authentify an \msricrash user}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid dtLogin.}
\adddoublerow{dtLongitude}{used to define a longitude value of a geograpical positions on earth. }
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid dtLongitude.}
\adddoublerow{dtPassword}{a password string used to authentify an \msricrash user}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid dtPassword.}
\adddoublerow{dtPhoneNumber}{a string used to store the phone number from the human declaring the crisis or the alert.}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid dtPhoneNumber.}
\adddoublerow{dtSmsCode}{A six-digit code send by sms to confirm the login.}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{}
\end{datadictionary}


\begin{datadictionary}
\addheading{Enumerations}

\adddoublerow{etAlertStatus}{
this type is used to indicate the different validation status of an alert.
}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which litteral belongs to the enumeration.}
\adddoublerow{etCrisisStatus}{
this type is used to indicate the different handling status of a crisis.
}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which litteral belongs to the enumeration.}
\adddoublerow{etCrisisType}{
this type is used to indicate the different types of a crisis.
}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which litteral belongs to the enumeration.}
\adddoublerow{etExpertise}{}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{}
\adddoublerow{etHumanKind}{
this type is used to indicate the kind of human that informs about a car crash crisis.
}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which litteral belongs to the enumeration.}
\end{datadictionary}





